Should I Airbnb My Property?

### 2017-03-10 abb_Writeup.Rmd
adding output for shiny example
Fix writeup from Booking bug

We will begin our analysis by making a comparison of the short and long-term markets at the metropolitan level.  Of our sample of 5,783 short-term rental units, 1,600 or 31.6\% of those units recorded a net revenue greater than what would likely have been garnered in the long-term market.

@@

<!-- ```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE} -->

<!--  ## Create dataset -->

<!--   type.data.ic <- str.data.ic -->

<!--   # Id the types -->
<!--   apt.id <- which(str.data.ic$type == 'Apartment') -->
<!--   house.id <- which(str.data.ic$type == 'House') -->

<!--   # Recalculate the percentiles -->
<!--   type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id], -->
<!--                                       return.type='rank') -->
<!--   type.data.ic$occ.qtl[house.id] <- makeWtdQtl( -->
<!--     type.data.ic$occ.rate[house.id], return.type='rank') -->

<!--   type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id], -->
<!--                                   return.type='rank') -->
<!--   type.data.ic$rate.qtl[house.id] <- makeWtdQtl( -->
<!--     type.data.ic$med.rate[house.id], return.type='rank') -->

<!--  ## Calc the occ rate numbers -->

<!--   ptrocc <- abbPrefPlot(type.data.ic, -->
<!--                          x.field='occ.rate', -->
<!--                          split.field='type', -->
<!--                          smooth=TRUE, -->
<!--                          smooth.span=.5 , -->
<!--                          spl.col=c('black', 'grey40')) -->

<!--   ptqocc <- abbPrefPlot(type.data.ic, -->
<!--                          x.field='occ.qtl', -->
<!--                          split.field='type', -->
<!--                          smooth=TRUE, -->
<!--                          smooth.span=.5 , -->
<!--                          spl.col=c('black', 'grey40')) -->

<!-- ``` -->

@@

Next, we divide the data into the five geographic sub-market shown in \autoref{pointmaps}. Within the City-Core, greater than one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.  That figure drops to three in ten for rural, one in four for beach , one in fix for other city location and about one in six for suburban locations.

@@

The analyses above show that, overall, just less than one out of every four short-term rental properties was actually more profitable as a short-term rental than it would have been if rented long-term over the course of the year. This proportion, however, varied by location and property type, with apartments and city-core properties showing the highest likelihood of short-term preference. While illustrative, the above do not fully control for property characteristics or owner actions -- which are a key component of short-term rental success.  To better understand which factors are related to a higher likelihood of short-term preference, we develop a set of logistic regression models below.

@@

Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (\autoref{revdens}).  However, there is a long right tail to the distibution of short-term revenues suggesting that some owners are doing better, and occasionally much better, in the short-term market than they would on the long-term market. This univariate comparison of revenues does not tell the entire story, as the Airbnb market does not have the same spatial distribution as the long-term market (Figure 8).  Short-term leasing is much more common in the central areas of the city, with small clusters showing up in suburban beach locations and rural tourist destinations like the Yarra Valley wine district.

@@

In short, about 30\% of current Airbnb properties are outperforming their potential in the long-term market.  If owners all operated as profit maximizers this figure could be 50\% or higher given that the overall demand for short-term rental could match the assumed supply increase in such a case.

>>>>

We will begin our analysis by making a comparison of the short and long-term markets at the metropolitan level.  Of our sample of 5,783 short-term rental units, 1,600 or 27.7\% of those units recorded a net revenue greater than what would likely have been garnered in the long-term market.

@@

@@

Next, we divide the data into the five geographic sub-market shown in \autoref{pointmaps}. Within the City-Core, greater than one out of three short-term properties brought in more net revenue than they likely would have under a long-term leasing scenario.  That figure drops to one in four for beach and rural, one in six for other city location and about one in nine for suburban locations.

@@

The analyses above show that, overall, more than one out of every four short-term rental properties was actually more profitable as a short-term rental than it would have been if rented long-term over the course of the year. This proportion, however, varied by location and property type, with apartments and city-core properties showing the highest likelihood of short-term preference. While illustrative, the above do not fully control for property characteristics or owner actions -- which are a key component of short-term rental success.  To better understand which factors are related to a higher likelihood of short-term preference, we develop a set of logistic regression models below.

@@

Comparing annual revenues from the two leasing strategies shows that revenues from more traditional long-term rentals are, on average, higher and much less variable than those from the Airbnb market (\autoref{revdens}).  However, there is a long right tail to the distribution of short-term revenues suggesting that some owners are doing better, and occasionally much better, in the short-term market than they would on the long-term market. This univariate comparison of revenues does not tell the entire story, as the Airbnb market does not have the same spatial distribution as the long-term market (Figure 8).  Short-term leasing is much more common in the central areas of the city, with small clusters showing up in suburban beach locations and rural tourist destinations like the Yarra Valley wine district.

@@

In short, about 28\% of current Airbnb properties are outperforming their potential in the long-term market.  If owners all operated as profit maximizers this figure could be 50\% or higher given that the overall demand for short-term rental could match the assumed supply increase in such a case.
